Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-14 IEEE_ConferenceOnGames/article_english.tex
Update to abstract 14/5 15:16

\author{\IEEEauthorblockN{ Jaime Salinas-Hernández}
\IEEEauthorblockA{\textit{Department of Graduate Studies} \\
\textit{Tijuana Institute of Technology}\\
Tijuana, México \\
salinas.jaime1217@gmail.com}
\and
\IEEEauthorblockN{ Mario Garcia-Valdez} \IEEEauthorblockA{\textit{Department of Graduate Studies} \\
\textit{Tijuana Institute of Technology}\\
Tijuana, México \\
mario@tectijuana.edu.mx}
\and
\IEEEauthorblockN{ Given Name Surname} \IEEEauthorblockA{\textit{dept. name of
organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}}

@@

\begin{abstract}
% We do not say this project, is more like: In this paoer an evolutionary ... 
% is presented or In this paper we present a .... (in third or first person plural) - MG   
In this paper an evolutionary computation-based system is proposed to generate 
levels for the Angry Birds video game, the levels themselves are composed of a 
set of birds that the player can use, a certain amount of pigs that must be destroyed 
in order to progress to the next level and a given number of pieces that conform 
structures that may or may not protect the pigs from the player. The focus in this stage
is the generation of diverse structures that can be played in the game having the
additional characteristics of being interesting and playable. We propose a 
multi-layered search, first contructing composite structures from basic components, to then
build more complex structures building from these components, following an open-ended 
evolution approach; in which the evolution of structures is not guided towards 
a single objective but rather is free to evolve and generate novelty or diversity. 
The objective is then that the proposed levels are evaluated by how complex they become and how 
different they are from the rest of the group.
%The experiments conducted show  
% We found that in the experiments conducted, levels generated where ...

@@

>>>>

\author{\IEEEauthorblockN{ Jaime Salinas-Hernández}
\IEEEauthorblockA{\textit{Department of Graduate Studies} \\
\textit{Tijuana Institute of Technology}\\
Tijuana, México \\
salinas.jaime1217@gmail.com}
\and
\IEEEauthorblockN{ Mario Garcia-Valdez} \IEEEauthorblockA{\textit{Department of Graduate Studies} \\
\textit{Tijuana Institute of Technology}\\
Tijuana, México \\
mario@tectijuana.edu.mx}
\and
\IEEEauthorblockN{ JJ Merelo} \IEEEauthorblockA{\textit{Department of Graduate Studies} \\
\textit{Universidad de Granada}\\
Granada, Spain\\
jmerelo@ugr.es}}

@@

\begin{abstract}
% We do not say this project, is more like: In this paoer an evolutionary ... 
% is presented or In this paper we present a .... (in third or first person plural) - MG   
In this paper an evolutionary computation-based system is proposed to generate 
levels for the Angry Birds video game, the levels themselves are composed of a 
set of birds that the player can use, a certain amount of pigs that must be destroyed 
in order to progress to the next level and a given number of pieces that conform 
structures that may or may not protect the pigs from the player. The focus in this stage
is the generation of diverse structures that can be played in the game having the
additional characteristics of being interesting and playable. We propose a 
multi-layered search, first contructing composite structures from basic components, to then
build more complex structures building from these components, following an open-ended 
evolution approach; in which the evolution of structures is not guided towards 
a single objective but rather is free to evolve and generate novelty or diversity. 
The objective is then that the proposed levels are evaluated by how complex they become and how 
different they are from the rest of the group. The experiments conducted show that a evolutionary approach allows the generated levels
to have a level of uniqueness because on most of the cases the way they are presented on screen
is a way a normal human would have trouble to create but at the same time are interesting to see.
% Maybe like this ? JSH
%The experiments conducted show  
% We found that in the experiments conducted, levels generated where ...

@@

% What is learned?
In this work we found that an evolutionary algorithm can be used to create 
this type of content not only because it is able to create levels that are interesting 
and diverse but because an evolutionary algorithm is capable of creating things a 
normal human could have trouble imagining of.
